Symbolic Abstract Data Type Inference

### 2015-07-06 motivation.tex
Patterns example in overview.

>>>>

\begin{figure}
  \begin{minipage}[b]{0.49\linewidth}
    \begin{verbatim}
[1:X] remove => 1  #
---
[1:1] add(1)           #
[2:2] remove => empty    #
---
[1:2] remove => 1  #
[2:2] add(1)         #
---
[1:1] add(1)       #
[2:2] add(2)         #
[3:2] remove => 2      #
---
[1:1] add(1)       #
[2:1] remove => 1    #
[3:1] remove => 1      #
---
[1:1] add(1)           #
[2:2] remove => empty    #
[3:1] remove => 1          #
---
[1:1] add(1)       #
[2:2] add(2)         #
[3:2] remove => 2      #
[4:1] remove => 1        #
    \end{verbatim}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.49\linewidth}
    \begin{verbatim}
[1:1] add(1)       #
[2:X] remove => 2    #
---
[1:X] remove => 1  #
[2:X] remove => 1    #
---
[1:X] remove => 1      #
[2:2] remove => empty    #
---
[1:1] remove => empty  #
[2:X] remove => 1        #
---
[1:1] add(1)       #
[2:2] add(2)         #
[3:X] remove => 3      #
---
[1:1] add(1)           #
[2:2] add(2)             #
[3:3] remove => empty      #
---
[1:1] add(1)       #
[2:1] remove => 1    #
[3:X] remove => 2      #
    \end{verbatim}
  \end{minipage}
  \caption{Invalid sequences according to the atomic queue ADT. The histories
  on the right are each redundant with some history on the left, and those on
  the left constitute a complete set.}
  \label{fig:patterns}
\end{figure}
